### 2023-03-29 response-to-audit-report.md

+-- | Generate a simple notification.
+simpleChoice :: Gen MarloweContext
+simpleChoice =
+  do
+    context <- arbitrary
+    choiceId <- semiArbitrary context
+    value <- semiArbitrary context
+    bound <- Bound <$> ((value -) <$> arbitraryPositiveInteger) <*> ((value +) <$> arbitraryPositiveInteger)
+    let
+      modifyContract (_, POSIXTime intervalEnd) contract =
+        do
+          let
+            timeout = POSIXTime $ intervalEnd + 1
+          contract' <- When [] timeout <$> semiArbitrary context
+          pure $ When [Case (Choice choiceId [bound]) contract'] timeout contract
+      modifyInput (TransactionInput interval _) = pure $ TransactionInput interval [NormalInput $ IChoice choiceId value]
+    simpleTransaction context modifyContract pure modifyInput
+
+
+-- | Generate a simple notification.
+simpleNotify :: Gen MarloweContext
+simpleNotify =
+  do
+    context <- arbitrary
+    let
+      modifyContract (_, POSIXTime intervalEnd) contract =
+        do
+          let
+            timeout = POSIXTime $ intervalEnd + 1
+          contract' <- When [] timeout <$> semiArbitrary context
+          pure $ When [Case (Notify TrueObs) contract'] timeout contract
+      modifyInput (TransactionInput interval _) = pure $ TransactionInput interval [NormalInput INotify]
+    simpleTransaction context modifyContract pure modifyInput
+
+
+-- | Generate a simple notification.
+simpleMerkleization :: Gen MarloweContext
+simpleMerkleization =
+  do
+    context <- arbitrary
+    mcState <- semiArbitrary context
+    intervalStart <- (getPOSIXTime (minTime mcState) +) <$> arbitraryPositiveInteger
+    intervalEnd <- (intervalStart +) <$> arbitraryPositiveInteger
+    let
+      interval = (POSIXTime intervalStart, POSIXTime intervalEnd)
+    timeout <- (intervalEnd +) <$> arbitraryPositiveInteger
+    contract <- When [] (POSIXTime timeout) <$> semiArbitrary context
+    let
+      DatumHash hash = datumHash . Datum $ toBuiltinData contract
+      mcInput = TransactionInput interval [MerkleizedInput INotify hash contract]
+    mcContract <- When [MerkleizedCase (Notify TrueObs) hash] (POSIXTime timeout) <$> semiArbitrary context
+    let
+      mcOutput = computeTransaction mcInput mcState mcContract
+    pure MarloweContext{..}

 -- | Recompute the output of a Marlowe transaction in an transaction context.
@@ -543,6 +689,27 @@ requireAmbiguousTimeout =
   >> requireNextTimeout `requireLE` view latestTime

+-- | Require a payment to a party.
+requirePayout :: Testify ()
+requirePayout =
+  let
+    isPayout (Payment _ (Party _) _ i) = i > 0
+    isPayout _ = False
+  in
+    view payments >>= "Positive payout" `require` any isPayout
+
+
+-- | Require not deposits.
+requireNoDeposits :: Testify ()
+requireNoDeposits =
+  let
+    isDeposit (NormalInput (IDeposit _ _ _ i)) = i > 0
+    isDeposit (MerkleizedInput (IDeposit _ _ _ i) _ _) = i > 0
+    isDeposit _ = False
+  in
+    view inputs >>= "No deposits" `require` (not . any isDeposit)
+
+
 -- | Throw an error unless a condition holds.
 throwUnless :: MonadError String m
             => String
@@ -671,30 +838,31 @@ checkContinuation expected =
 data TransactionTest =
   TransactionTest
   {
-    name          :: String
-  , generator     :: Gen MarloweContext
-  , precondition  :: Testify ()
-  , invariant     :: [Invariant]
-  , postcondition :: Testify ()
+    name           :: String
+  , generator      :: Gen MarloweContext
+  , precondition   :: Testify ()
+  , invariant      :: [Invariant]
+  , postcondition  :: Testify ()
+  , allowShrinkage :: Bool
   }

 instance Default TransactionTest where
   def =
     TransactionTest
     {
-      name          = mempty
-    , generator     = arbitrary
-    , precondition  = pure ()
-    , invariant     = mempty
-    , postcondition = pure ()
+      name           = mempty
+    , generator      = arbitrary
+    , precondition   = pure ()
+    , invariant      = mempty
+    , postcondition  = pure ()
+    , allowShrinkage = True
     }

 -- | Test a Marlowe transaction.
-test :: Bool             -- ^ Whether to perform shrinkage of generated values.
-     -> TransactionTest  -- ^ The test.
+test :: TransactionTest  -- ^ The test.
      -> TestTree         -- ^ The result.
-test doShrink TransactionTest{..} =
+test TransactionTest{..} =
   testProperty name
     . property
     $ let
@@ -707,7 +875,7 @@ test doShrink TransactionTest{..} =
             Right () -> True   -- Test passed.
         gen = generator `suchThat` preResolve precondition
       in
-        (if doShrink then forAllShrink gen shrink else forAll gen)
+        (if allowShrinkage then forAllShrink gen shrink else forAll gen)
           . postResolve
           $ mapM_ checkInvariant invariant >> postcondition

@@ -858,11 +1026,128 @@ anyInput =
   }

+-- | Test that payments substract value from internal accounts.
+payingSubtractsFromAccount :: TransactionTest
+payingSubtractsFromAccount =
+  def
+  {
+    name           = "Paying subtracts from account"
+  , allowShrinkage = False
+  , generator      = simplePayment
+  , postcondition  = do
+                       delta <-
+                         fmap (AM.filter (/= 0))
+                           $ AM.unionWith (+)
+                           <$> view preAccounts
+                           <*> (AM.fromList . fmap (second negate) . AM.toList <$> view postAccounts)
+                       require "Only one balance changes." ((== 1) . length . AM.toList) delta
+                       require "Some balance decreases." (all (> 0) . AM.elems) delta
+  }
+
+
+-- | Test that deposits add value to internal accounts.
+depositAddsToAccount :: TransactionTest
+depositAddsToAccount =
+  def
+  {
+    name           = "Deposit adds to account"
+  , allowShrinkage = False
+  , generator      = simpleDeposit
+  , postcondition  = do
+                       delta <-
+                         fmap (AM.filter (/= 0))
+                           $ AM.unionWith (+)
+                           <$> view postAccounts
+                           <*> (AM.fromList . fmap (second negate) . AM.toList <$> view preAccounts)
+                       require "Only one balance changes." ((== 1) . length . AM.toList) delta
+                       require "Some balance increases." (all (> 0) . AM.elems) delta
+  }
+
+
+-- | Test that notify contines as expected
+notifyContinues :: TransactionTest
+notifyContinues =
+  def
+  {
+    name           = "Notify continues as expected"
+  , allowShrinkage = False
+  , generator      = simpleNotify
+  , postcondition  = view preContract >>=
+                       \case
+                         When [Case (Notify TrueObs) contract] _ _ -> checkContinuation contract
+                         _ -> throwError "Test setup failed."
+  }
+
+
+-- | Test that choice continues as expected.
+choiceContinues :: TransactionTest
+choiceContinues =
+  def
+  {
+    name           = "Choice continues as expected"
+  , allowShrinkage = False
+  , generator      = simpleChoice
+  , postcondition  = view preContract >>=
+                       \case
+                         When [Case (Choice _ _) contract] _ _ -> checkContinuation contract
+                         _ -> throwError "Test setup failed."
+  }
+
+
+-- | Test that deposit continues as expected.
+depositContinues :: TransactionTest
+depositContinues =
+  def
+  {
+    name           = "Deposit continues as expected"
+  , allowShrinkage = False
+  , generator      = simpleDeposit
+  , postcondition  = view preContract >>=
+                       \case
+                         When [Case Deposit{} contract] _ _ -> checkContinuation contract
+                         _ -> throwError "Test setup failed."
+  }
+
+
+-- | Test that deposit continues as expected.
+merkleizationContinues :: TransactionTest
+merkleizationContinues =
+  def
+  {
+    name           = "Merkleization continues as expected"
+  , allowShrinkage = False
+  , generator      = simpleMerkleization
+  , postcondition  = view inputs >>=
+                       \case
+                         [MerkleizedInput INotify _ contract] -> checkContinuation contract
+                         _ -> throwError "Test setup failed."
+  }
+
+
+-- | Test that deposit continues as expected.
+choiceSets :: TransactionTest
+choiceSets =
+  def
+  {
+    name           = "Choice records the value of the choice"
+  , allowShrinkage = False
+  , generator      = simpleChoice
+  , postcondition  = view inputs >>=
+                       \case
+                         [NormalInput (IChoice choiceId value)] ->
+                           do
+                             choices' <- choices <$> view postState
+                             unless (AM.lookup choiceId choices' == Just value)
+                               $ throwError "Choice missing from state"
+                         _ -> throwError "Test setup failed."
+  }
+
+
 -- | Run the tests.
 tests :: TestTree
 tests =
   testGroup "Compute Transaction"
-    $ fmap (test True)
+    $ test <$>
     [
       invalidInterval
     , tooEarly
@@ -875,4 +1160,11 @@ tests =
     , ifBranches
     , assertWarns
     , anyInput
+    , payingSubtractsFromAccount
+    , depositAddsToAccount
+    , depositContinues
+    , choiceContinues
+    , notifyContinues
+    , choiceSets
+    , merkleizationContinues
     ]
diff --git a/marlowe-test/src/Spec/Marlowe/Semantics/Functions.hs b/marlowe-test/src/Spec/Marlowe/Semantics/Functions.hs
index 25fbef841..9a3c8acdc 100644
--- a/marlowe-test/src/Spec/Marlowe/Semantics/Functions.hs
+++ b/marlowe-test/src/Spec/Marlowe/Semantics/Functions.hs
@@ -100,6 +100,7 @@ tests =
         testProperty "Invalid interval" $ checkFixInterval True  False
       , testProperty "Interval in past" $ checkFixInterval False True
       , testProperty "Interval trimmed" $ checkFixInterval False False
+      , testProperty "Invalid interval in past" $ checkFixInterval True True
       ]
     , testGroup "evalValue"
       [
@@ -218,14 +219,22 @@ forAll' = flip forAllShrink shrink
 --   generating arbitrary valid and invalid intervals and checking that
 --   results or errors re reported correctly.
 checkFixInterval :: Bool      -- ^ Whether the validity interval should be invalid.
-                 -> Bool      -- ^ Whethe the validity interval should be in the past.
+                 -> Bool      -- ^ Whether the validity interval should be in the past.
                  -> Property  -- ^ The test.
 checkFixInterval invalid inPast =
   property $ do
   let gen = do
         state <- arbitrary
-        end   <- arbitrary `suchThat` (\t -> (t < minTime state) == inPast)
-        start <- arbitrary `suchThat` (\t -> (t > end) == invalid && (t < minTime state) == inPast)
+        (start, end) <-
+          case (invalid, inPast) of
+            (True, True) -> do
+                              start' <- arbitrary `suchThat` (< minTime state)
+                              end'   <- arbitrary `suchThat` (< start')
+                              pure (start', end')
+            _            -> do
+                              end'   <- arbitrary `suchThat` (\t -> (t < minTime state) == inPast)
+                              start' <- arbitrary `suchThat` (\t -> (t > end') == invalid && (t < minTime state) == inPast)
+                              pure (start', end')
         pure ((start, end), state)
   forAll' gen $ \(interval, state) ->
     case fixInterval interval state of
diff --git a/marlowe-test/src/Spec/Marlowe/Semantics/Golden.hs b/marlowe-test/src/Spec/Marlowe/Semantics/Golden.hs
index 9025906ad..72d052fb7 100644
--- a/marlowe-test/src/Spec/Marlowe/Semantics/Golden.hs
+++ b/marlowe-test/src/Spec/Marlowe/Semantics/Golden.hs
@@ -40,6 +40,7 @@ import Test.Tasty.HUnit (assertBool, testCase)

 import qualified PlutusTx.AssocMap as AM (empty)
 import qualified Spec.Marlowe.Semantics.Golden.Escrow as Escrow (contract, invalids, valids)
+import qualified Spec.Marlowe.Semantics.Golden.Negative as Negative (contract, invalids, valids)
 import qualified Spec.Marlowe.Semantics.Golden.Pangram as Pangram (contract, invalids, valids)
 import qualified Spec.Marlowe.Semantics.Golden.Swap as Swap (contract, invalids, valids)
 import qualified Spec.Marlowe.Semantics.Golden.Trivial as Trivial (contract, invalids, valids)
@@ -59,6 +60,7 @@ goldenContracts =
   , Swap.contract
   , Trivial.contract
   , ZCB.contract
+  , Negative.contract
   -- Note that Pangram is omitted because `getAllInputs` takes 30 minutes for it.
   ]

@@ -68,11 +70,12 @@ tests :: TestTree
 tests =
   testGroup "Golden"
     [
-      testGolden "Escrow"           _GENERATE_TEST_CASES_ Escrow.contract  Escrow.valids  Escrow.invalids
-    , testGolden "Pangram"          _GENERATE_TEST_CASES_ Pangram.contract Pangram.valids Pangram.invalids
-    , testGolden "Swap"             _GENERATE_TEST_CASES_ Swap.contract    Swap.valids    Swap.invalids
-    , testGolden "Trivial"          _GENERATE_TEST_CASES_ Trivial.contract Trivial.valids Trivial.invalids
-    , testGolden "Zero Coupon Bond" _GENERATE_TEST_CASES_ ZCB.contract     ZCB.valids     ZCB.invalids
+      testGolden "Escrow"           _GENERATE_TEST_CASES_ Escrow.contract   Escrow.valids   Escrow.invalids
+    , testGolden "Pangram"          _GENERATE_TEST_CASES_ Pangram.contract  Pangram.valids  Pangram.invalids
+    , testGolden "Swap"             _GENERATE_TEST_CASES_ Swap.contract     Swap.valids     Swap.invalids
+    , testGolden "Trivial"          _GENERATE_TEST_CASES_ Trivial.contract  Trivial.valids  Trivial.invalids
+    , testGolden "Zero Coupon Bond" _GENERATE_TEST_CASES_ ZCB.contract      ZCB.valids      ZCB.invalids
+    , testGolden "Negative"         _GENERATE_TEST_CASES_ Negative.contract Negative.valids Negative.invalids
     ]

@@ -125,7 +128,7 @@ testInvalid :: Contract -> [GoldenCase] -> IO ()
 testInvalid = testValidity False

--- | Test erroneous transactions for the Pangram contract.
+-- | Test erroneous transactions for a contract.
 testValidity :: Bool          -- ^ Whether the test cases should pass.
              -> Contract      -- ^ The contract.
              -> [GoldenCase]  -- ^ The test cases.
@@ -148,11 +151,12 @@ goldenTransactions :: [[GoldenTransaction]]
 goldenTransactions =
   uncurry validTransactions
     <$> [
-          (Escrow.contract , Escrow.valids )
-        , (Pangram.contract, Pangram.valids)
-        , (Swap.contract   , Swap.valids   )
-        , (Trivial.contract, Trivial.valids)
-        , (ZCB.contract    , ZCB.valids    )
+          (Escrow.contract  , Escrow.valids  )
+        , (Pangram.contract , Pangram.valids )
+        , (Swap.contract    , Swap.valids    )
+        , (Trivial.contract , Trivial.valids )
+        , (ZCB.contract     , ZCB.valids     )
+        , (Negative.contract, Negative.valids)
         ]

diff --git a/marlowe-test/src/Spec/Marlowe/Semantics/Golden/Negative.hs b/marlowe-test/src/Spec/Marlowe/Semantics/Golden/Negative.hs
new file mode 100644
index 000000000..eea8fa414
--- /dev/null
+++ b/marlowe-test/src/Spec/Marlowe/Semantics/Golden/Negative.hs
@@ -0,0 +1,151 @@
+-----------------------------------------------------------------------------
+--
+-- Module      :  $Headers
+-- License     :  Apache 2.0
+--
+-- Stability   :  Experimental
+-- Portability :  Portable
+--
+-- | Reference golden output for a contract with negative deposits.
+--
+-----------------------------------------------------------------------------
+
+
+{-# LANGUAGE NumericUnderscores #-}
+{-# LANGUAGE OverloadedStrings #-}
+{-# LANGUAGE TypeSynonymInstances #-}
+
+
+module Spec.Marlowe.Semantics.Golden.Negative
+  ( -- * Contracts
+    contract
+    -- * Test cases
+  , invalids
+  , valids
+  ) where
+
+
+import Language.Marlowe.Core.V1.Semantics
+  (Payment(Payment), TransactionInput(..), TransactionOutput(..), TransactionWarning(TransactionNonPositiveDeposit))
+import Language.Marlowe.Core.V1.Semantics.Types
+  ( Action(Choice, Deposit, Notify)
+  , Bound(..)
+  , Case(Case)
+  , ChoiceId(..)
+  , Contract(Close, Let, When)
+  , Input(NormalInput)
+  , InputContent(IChoice, IDeposit, INotify)
+  , Observation(ValueEQ, ValueGT, ValueLT)
+  , Party
+  , Payee(Party)
+  , State(State, accounts, boundValues, choices, minTime)
+  , Token(..)
+  , Value(ChoiceValue, Constant)
+  )
+import Language.Marlowe.Util ()
+import Plutus.V2.Ledger.Api (POSIXTime(..))
+
+import qualified PlutusTx.AssocMap as AM (Map, fromList)
+
+
+party :: Party
+party = "Party"
+
+counterparty :: Party
+counterparty = "Counterparty"
+
+ada :: Token
+ada = Token "" ""
+
+
+-- | The Zero-Coupon Bond contract.
+contract :: Contract
+contract =
+  let
+    initial = Constant 2_000_000
+    choice = ChoiceId "Deposit" party
+    value = ChoiceValue choice
+    initialDeadline = 1000
+    choiceDeadline = 2000
+    notifyDeadline = 3000
+    depositDeadline = 4000
+  in
+    When
+      [
+        Case (Deposit counterparty counterparty ada initial)
+          $ When
+              [
+                Case (Choice choice [Bound (-1) 1])
+                  $ When
+                    [
+                      Case (Deposit party counterparty ada value)
+                        Close
+                    , Case (Notify $ ValueGT value $ Constant 0)
+                       $ Let "Positive" (Constant 1)
+                       $ When
+                         [
+                           Case (Deposit party counterparty ada value)
+                             Close
+                         ]
+                         depositDeadline
+                         Close
+                    , Case (Notify $ ValueEQ value $ Constant 0)
